\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1.9cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{microtype}

% ---- Colors & links -------------------------------------------------------
\definecolor{linkblue}{HTML}{286DC0}
\hypersetup{colorlinks=true, urlcolor=linkblue, linkcolor=linkblue, citecolor=linkblue}

% ---- Page setup -----------------------------------------------------------
\pagenumbering{gobble}
\setlength{\parindent}{0pt}

% ---- Section headings: bold, rule underneath ------------------------------
\titleformat{\section}{\large\bfseries}{}{0em}{}[\vspace{-3pt}\titlerule]
\titlespacing{\section}{0pt}{8pt}{5pt}

% ---- Tight, consistent bullet lists ---------------------------------------
\setlist[itemize]{leftmargin=1.4em, topsep=2pt, itemsep=1.5pt, parsep=0pt,
                  label=\textbullet}

% ---- Hanging-indent entry for publications / patents ----------------------
% First line flush left (author names align at the margin); wrapped lines indent.
\newcommand{\pubitem}[1]{\par\noindent\hangindent=1.6em\hangafter=1 #1\par\addvspace{3pt}}

\begin{document}

% ===== Header ==============================================================
\begin{center}
  {\huge\bfseries Tao Chen}\\[0.3em]
  {\itshape\small Optical thermal metrology \ \textperiodcentered\ \ micro/nanoscale heat transport}\\[0.55em]
  \faEnvelope\ \href{mailto:torin.chen@yale.edu}{torin.chen@yale.edu}
  \quad\textbullet\quad
  \faGraduationCap\ \href{https://scholar.google.com/citations?user=wLh8cHgAAAAJ&hl=en}{Google Scholar}
\end{center}

% ===== Education ===========================================================
\section{Education}

\textbf{M.Eng.\ in Energy and Power Engineering} \hfill 2023 -- 2026\\
Huazhong University of Science and Technology \ \textbar\ \ Advisor: Prof.\ Puqing Jiang
\begin{itemize}
  \item Admitted ranked 1st in the entrance examination, with a perfect score in mathematics.
  \item Thesis: Development and application of a thermal-property measurement technique based on the square-pulsed source (SPS) method.
  \item Selected coursework: Theory and Engineering Applications of Heat Transfer; Advanced Applied Engineering Mathematics; Thermal Signal Processing and Visualization; Modern Instrumental Analysis Methods; Academic Writing.
\end{itemize}

\vspace{2pt}
\textbf{B.Eng.\ in Energy and Power Engineering} \hfill 2019 -- 2023\\
Huazhong University of Science and Technology
\begin{itemize}
  \item Thesis: Development and application of an infrared-based AC calorimetry system.
  \item Selected coursework: Engineering Heat Transfer; Engineering Thermodynamics; Engineering Numerical Methods; Calculus; Linear Algebra; Probability and Statistics.
\end{itemize}

% ===== Research Interests ==================================================
\section{Research Interests}
\begin{itemize}
  \item Optical thermal metrology (TDTR, FDTR, SDTR, and the square-pulsed source method) for micro/nanoscale heat transfer and non-equilibrium thermal transport.
  \item Thermal characterization of thin films, interfaces, anisotropic and two-dimensional materials, liquids, and thermal interface materials.
  \item Inverse problems, uncertainty quantification, and the interplay between heat transfer and applied mathematics.
\end{itemize}

% ===== Research Experience =================================================
\section{Research Experience}

\textbf{Optical Measurement of Multilayer-Film Thermal Properties in Chips} \hfill 2025 -- Present\\
\textit{Huazhong University of Science and Technology (with an industry partner)}
\begin{itemize}
  \item Measure the thermal conductivity and volumetric heat capacity of each micron-thick layer in multilayer chip stacks.
  \item Built the optical platform and an automated routine for spatial thermal-property mapping.
\end{itemize}

\vspace{2pt}
\textbf{Near-Junction Thermal Transport in GaN Devices} \hfill 2024 -- Present\\
\textit{Huazhong University of Science and Technology}
\begin{itemize}
  \item Developed the square-pulsed source (SPS) thermoreflectance method (see Publications).
  \item Extending it to an ultraviolet square-pulse transient scheme for \emph{in situ}, near-junction measurements.
  \item Quantifying how growth conditions set the thermal resistance of passivation layers and interfaces.
\end{itemize}

\vspace{2pt}
\textbf{Micro/Nanoscale Thermal Characterization for 3D-Stacked Chips} \hfill 2024\\
\textit{Huazhong University of Science and Technology (with an industry partner)}
\begin{itemize}
  \item Designed and built an optical micro/nanoscale thermal-characterization platform with $<$10\% measurement error and automated spatial mapping.
  \item Linked micro/nanoscale structural features to thermal transport across real chip samples to inform 3D-stacked chip design.
\end{itemize}

% ===== Honors and Awards ===================================================
\section{Honors and Awards}
\begin{itemize}[label={}, leftmargin=0pt, itemsep=2.5pt]
  \item National Graduate Scholarship, Ministry of Education of China (national) \hfill Dec 2025
  \item First-Class Postgraduate Scholarship, Huazhong University of Science and Technology \hfill Dec 2025
  \item National Graduate Scholarship, Ministry of Education of China (national) \hfill Dec 2024
  \item First-Class Postgraduate Scholarship, Huazhong University of Science and Technology \hfill Dec 2024
  \item Merit Student, Huazhong University of Science and Technology \hfill Dec 2024
  \item Outstanding Conference Paper Award, 3rd Chinese Conference on Thermal Properties \hfill Jun 2024
  \item Self-Reliance Scholarship, School of Energy and Power Engineering \hfill Feb 2020
\end{itemize}

% ===== Professional Service ================================================
\section{Professional Service}
Referee for \textit{Physical Review Letters}, \textit{Physical Review Applied}, and \textit{Physical Review Materials}.

% ===== Journal Articles ====================================================
\section{Journal Articles}

\pubitem{\textbf{Chen, T.}, Xiao, B., Qian, X., \& Jiang, P. (2026). Simultaneous measurement of pressure-dependent bulk and interfacial thermal properties in thermal interface materials using square-pulsed source thermoreflectance. \textit{Applied Thermal Engineering} (under review). arXiv:2603.22733.}

\pubitem{\textbf{Chen, T.}, Wang, D., \& Jiang, P. (2026). Physics-derived natural coordinates for fast uncertainty propagation in multilayer thermoreflectance. \textit{International Journal of Heat and Mass Transfer} (under review).}

\pubitem{\textbf{Chen, T.}, \& Jiang, P. (2025). Weak coupling of diffusional and phonon-like modes in liquids revealed by dynamic Kapitza length. \textit{Physical Review Letters} (under revision).}

\pubitem{Shen, Y., \textbf{Chen, T.}, Song, S., Zhang, K., Chen, Y., Zhao, L., \& Jiang, P. (2026). Mechanistic insight into BEOL thermal transport via optical metrology and multiphysics simulation. \textit{International Communications in Heat and Mass Transfer}, 111751.}

\pubitem{\textbf{Chen, T.}, \& Jiang, P. (2025). Universal thermometry of solid--liquid interfacial thermal conductance. \textit{Applied Physics Letters}, 127, 191608. [Featured Article]}

\pubitem{Bao, Y., \textbf{Chen, T.}, Miao, Z., Zheng, W., Jiang, P., Chen, K., Guo, R., \& Xue, D. (2025). Machine-learning-assisted understanding of depth-dependent thermal conductivity in lithium niobate induced by point defects. \textit{Advanced Electronic Materials}, 11(11), 2400944.}

\pubitem{Xiao, B., \textbf{Chen, T.}, Zhang, W., Qian, X., \& Jiang, P. (2025). Fast and reliable thermal property extraction from FDTR measurements via hybrid particle swarm optimization. \textit{International Journal of Heat and Mass Transfer}, 256, 128109.}

\pubitem{\textbf{Chen, T.}, \& Jiang, P. (2025). Simultaneous, non-contact measurement of liquid and interfacial thermal properties via a differential square-pulsed source method. \textit{Langmuir}, 41(38), 26496--26504.}

\pubitem{Zhang, K., \textbf{Chen, T.}, Ma, J., \& Jiang, P. (2025). A variable-spot-size and multi-frequency square-pulsed source (SPS) approach for comprehensive characterization of anisotropic thermal transport properties in multilayered thin films. \textit{Journal of Physics D: Applied Physics}, 58(32), 325302.}

\pubitem{Zhang, M., \textbf{Chen, T.}, Song, S., Bao, Y., Guo, R., Zheng, W., Jiang, P., \& Yang, R. (2025). Extending the low-frequency limit of time-domain thermoreflectance via periodic waveform analysis. \textit{Journal of Applied Physics}, 138(5), 055101.}

\pubitem{\textbf{Chen, T.}, \& Jiang, P. (2025). A measurement method for the thermal conductivity and specific heat of submillimeter-sized low-thermal-conductivity materials. \textit{Journal of Huazhong University of Science and Technology (Natural Science Edition)}, 53(7), 88--93.}

\pubitem{\textbf{Chen, T.}, \& Jiang, P. (2025). Decoupling thermal properties in multilayered systems for advanced thermoreflectance experiments. \textit{Physical Review Applied}, 23(4), 044004.}

\pubitem{Zhang, M., \textbf{Chen, T.}, Zeng, A., Tang, J., Guo, R., \& Jiang, P. (2025). Simultaneous measurement of thermal conductivity, heat capacity, and interfacial thermal conductance by leveraging negative delay-time data in time-domain thermoreflectance. \textit{Progress in Natural Science: Materials International}, 35(2), 375--384.}

\pubitem{Song, S., \textbf{Chen, T.}, \& Jiang, P. (2025). Comprehensive thermal property measurement of semiconductor heterostructures using the square-pulsed source (SPS) method. \textit{Journal of Applied Physics}, 137(5), 055101.}

\pubitem{\textbf{Chen, T.}, \& Jiang, P. (2025). An optical method for measuring local convective heat transfer coefficients over $100\,\mathrm{W/(m^2{\cdot}K)}$ with sub-millimeter resolution. \textit{Measurement}, 249, 117001.}

\pubitem{\textbf{Chen, T.}, \& Jiang, P. (2024). Unraveling the intrinsic relationship of thermal properties in thermoreflectance experiments. \textit{Acta Physica Sinica}, 73(23), 230202. [Cover Article]}

\pubitem{\textbf{Chen, T.}, Song, S., Hu, R., \& Jiang, P. (2024). Comprehensive measurement of the three-dimensional thermal conductivity tensor using a beam-offset square-pulsed source (BO-SPS) approach. \textit{International Journal of Thermal Sciences}, 207, 109347.}

\pubitem{\textbf{Chen, T.}, Song, S., Shen, Y., Zhang, K., \& Jiang, P. (2024). Simultaneous measurement of thermal conductivity and heat capacity across diverse materials using the square-pulsed source (SPS) technique. \textit{International Communications in Heat and Mass Transfer}, 158, 107849.}

% ===== Conference Presentations ===========================================
\section{Conference Presentations}

\pubitem{\textbf{Chen, T.}, \& Jiang, P. (2025, Oct.). Pressure-dependent thermal properties of thermal interface materials [oral presentation]. 9th Workshop on Thermal Transport (WTT 2025), China.}

\pubitem{\textbf{Chen, T.}, Hu, Z., \& Jiang, P. (2024, Dec.). Measurement of the three-dimensional anisotropic thermal conductivity tensor of micro-sized samples using the beam-offset square-pulsed source (BO-SPS) method; and Accurate measurement of the local intrinsic convective heat transfer coefficient using the square-pulsed source (SPS) method [two oral presentations]. Annual Conference on Heat and Mass Transfer, Chinese Society of Engineering Thermophysics, China.}

\pubitem{\textbf{Chen, T.}, \& Jiang, P. (2024, Sep.). Revealing the intrinsic relationship of thermal-property parameters in thermoreflectance experiments [oral presentation]. 3rd Chinese Conference on Thermal Properties, China. \textit{(Outstanding Conference Paper Award)}}

\pubitem{\textbf{Chen, T.}, Song, S., \& Jiang, P. (2024, Jun.). Advancing thermal characterization: simultaneous micrometer-scale measurement of thermal conductivity and heat capacity in low-conductivity materials using the square-pulsed source (SPS) technique [oral presentation]. 3rd Asian Conference on Thermal Sciences (ACTS 2024), Shanghai, China.}

% ===== Patents =============================================================
\section{Patents}

\pubitem{Jiang, P., \& \textbf{Chen, T.} (2025). Method and system for measuring the local convective heat transfer coefficient. Patent No.\ ZL 2024 1 0763998.4.}

\pubitem{Jiang, P., \textbf{Chen, T.}, \& Xiao, B. (2025). System and method for measuring the thermal properties of soft-matter thin films. Patent Application No.\ 2025109077810.}

\pubitem{Jiang, P., Yang, R., Song, S., \textbf{Chen, T.}, \& Wu, J. (2024). Method and system for measuring the anisotropic thermal properties of sub-millimeter-scale samples. Patent No.\ ZL 2024 1 0057927.2.}

% ===== Industry Experience ================================================
\section{Industry Experience}
\textbf{Engineering Intern}, Sichuan Air Separation Equipment (Group) Co., Ltd., Chengdu, China \hfill 2022
\begin{itemize}
  \item Studied the design and manufacture of cryogenic equipment (pressure vessels, compressors, heat exchangers) and the thermodynamics of air-separation units.
  \item Authored a technical report summarizing key engineering findings.
\end{itemize}

% ===== Skills ==============================================================
\section{Skills}
\textbf{Experimental:} Design, build, and calibrate optical thermal-metrology systems; TDTR, FDTR, SDTR, and SPS measurements.\\[2pt]
\textbf{Computational:} MATLAB, Python, COMSOL, Origin, \LaTeX, SolidWorks; modeling, inverse fitting, and uncertainty analysis.\\[2pt]
\textbf{Languages:} English (proficient), Mandarin (native).

\end{document}
